\speculake: Hiding Malware in Speculative Execution

### 2018-12-07 paper/payloads.tex
add new references and reference figure 6

We can overcome
this by having the trigger program communicate the decryption key to the payload
program via the branch predictor. To accomplish this, we use multiple speculative
entry points, each that derives a
different decryption key before calling a common decryption routine. Since
the exact speculative entry point is determined by the trigger program, an
analyst cannot discover the decryption key directly from the payload program.

@@

To increase security, we instead use nested speculation to \emph{chain} entry points
together. Rather than derive
the key from a single entry point, we have each potential entry point perform
another indirect jump that the CPU cannot immediately resolve, forcing it to
speculate while already executing speculatively. The predicted target of that jump
will also be determined by the trigger program. For example, if the trigger
program makes 30 training jumps, followed by 10 additional indirect jumps, and
the payload program performs the same 30 training jumps before a stall, the CPU
will predict the payload program will also perform the next 10 jumps. If each
jump has the potential to land in up to 1024 possible locations, this would
provide in total $1024^{10} = 2^{100}$ possible keys, or 100~bits of security.
We describe our implementation of nested speculative execution in
Section~\ref{subsec:impl-aes}, where we achieve 128~bits of security.
%Section~\ref{subsec:nested-spec}.

>>>>

We can overcome this by having the trigger program communicate the decryption
key to the payload program via the branch predictor. Previous work has analyzed
the capability of the branch predictor to distribute keys to other
programs~\cite{evtyushkin2016jump, lee2017inferring, aciiccmez2007predicting}
and demonstrated that this is not a secure method of key distribution. However,
the goal of using the branch predictor is not share a single secret via entry
point but rather to use multiple jumps to construct the decryption key
speculatively. To accomplish this, we use multiple speculative entry points,
each that derives a different decryption key before calling a common decryption
routine. Since the exact speculative entry point is determined by the trigger
program, an analyst cannot discover the decryption key directly from the payload
program.

@@

To increase security, we instead use nested speculation to \emph{chain} entry
points together. Rather than derive the key from a single entry point, we have
each potential entry point perform another indirect jump that the CPU cannot
immediately resolve, forcing it to speculate while already executing
speculatively. The predicted target of that jump will also be determined by the
trigger program. Meaning that an analyst that is (somehow, possibly via oracle,
or attacks similar to~\cite{aciiccmez2007predicting}) able to determine the
location of first speculative jump is still unable to reconstruct the whole key
as future speculative jumps are determined solely by the trigger program which
the analyst does not have access to.

For example, if the trigger program makes 30 training jumps, followed by 10
additional indirect jumps, and the payload program performs the same 30 training
jumps before a stall, the CPU will predict the payload program will also perform
the next 10 jumps. Speculatively the CPU will attempt to follow each of these
jumps speculatively.

If each jump has the potential to land in up to 1024 possible locations, this
would provide in total $1024^{10} = 2^{100}$ possible keys, or 100~bits of
security. We describe our implementation of nested speculative execution in
Section~\ref{subsec:impl-aes}, where we achieve 128~bits of security.
Figure~\ref{fig:nested-spec} demonstrates this in practice, the trigger program
running a series of training jumps followed by indirect jumps influences the
payload program to follow the same path. Any analyst attempting to follow this
path without the trigger program would need to correctly jump to each of the 10
addresses to load the correct key. The security gained here is not a result of a
single entry point remaining secret but rather multiple independent jumps by the
unknown trigger program providing numerous landing points for each jump.

\FigNestedSpec
